Understanding the impacts of video-guided activities on parent-child interaction

### 2019-09-28 paper/manuscript.Rmd
full draft -- rewrite discussion

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4510"

@@

Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The No Video condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the No Video condition received the same props but did not watch the activity video.
Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]). 
There were no significant effects of age, gender, or parent's level of education.
A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}

@@

We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

@@

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more. 
Looking at the most frequent content words parents used after the Activity Video, ...
In contrast, the most frequent content words parents used in the No Video condition were...

Parents who watched an activity video made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA than dyads in the no video condition.
No differences in the duration or number of episodes of passive or coordinated JA between conditions were found.

After the activity video, parents with higher RR scores showed an increased number of passive JA episodes than high-RR parents did after no video.
While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA. 
RELATE BACK TO HYPOTHESES

@@

Experiment 1 found that parents who watched an activity video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Parents who watched an activity video made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^4]

@@

The design of Experiment 2 was similar to that of Experiment 1, except that instead of No Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children. 
This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development. 
The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies. 
Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
Details of the videos used in the Activity Video conditions are in the Appendix.

@@

Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
We first report reregistered regressions predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
As noted in the preregistration, we adopt an alpha level of .005 for statistical significance and will report alphas between .05 and .005 as suggestive.

### Lexical Diversity
```{r, e2-lexdiv-regressions, echo=F, include=F}
# preregistered analyses:
# The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens). 
# 1) bids, 2) total JA eps, 3) # tokens 4) TTR -- alpha level = .005
# Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs. control) and age in months as fixed effects and participant and specific video as random effects. 
# DV ~ age * condition + (1 | participant) + (1 | video)
# Lab standard operating procedures will be used for random effects pruning in case of non-convergence.
# We will interpret condition main effects as well as age * condition interactions (positive or negative) as evidence for behavior changes caused by video scaffolding. 
# Because of the larger number of coefficients of interest (4 models x 2 coefficients), we will adopt an alpha level of .005 for statistical significance and will report alpha between .05 and .005 as suggestive.
# “secondary analyses"
# We will analyze the proportion of coordinated vs. passive joint attention separately using the same model specification.

@@

We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
There was suggestively lower TTR in the Video condition (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than in the Control condition (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]). 
There was no significant effect of age, nor a significant interaction.
The preregistered regression predicting the number of tokens used by parents revealed no significant effects. 
An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other significant effects on parental bids for JA.

@@

```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "The number of episodes of coordinated JA by condition and age in Experiment 2. Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition."}

@@

This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from a commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), but played with the same sets of toys given to those in the experimental conditions.
After completing the videos, parents were videotaped playing with their children for two minutes. 
The quality of parents' interactions with their children were measured by the lexical diversity of their child-directed speech, and through behavioral coding of bids for and episodes of joint attention (JA).

>>>>

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4569"

@@

Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
There was significantly lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]). 
There were no significant effects of age, gender, or parent's level of education.
A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).

@@

```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom). Error bars show bootstrapped 95\\% confidence intervals, and gray dots indicate values for each participant."}

@@

We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video. 
There were significantly more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]). 
Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.

@@

To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the differency in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot). 
Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "thank", "have", "which", and "school", while words that are most characteristic of the No Video condition include "ready", "on", "oh", "see", "going", "let", and "are".

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable: 
after the Activity Video, parents used more words related to requests (e.g., "Can I have X? / Give me X. Thank you!"), whereas after no intervention parents' language related more to invitations (e.g., "Are you ready?" / "Let's see.").
However, parents who watched an activity video also made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the no video condition.
In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.

@@

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words overall to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^4]

@@

The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children. 
This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development. 
The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies. 
Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
Details of the videos used in the Activity Video conditions are in the Appendix.

@@

Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
We first report preregistered regressions[^5] predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.

[^5]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression. Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).

### Lexical Diversity
```{r, e2-lexdiv-regressions, echo=F, include=F}
# preregistered analyses:
# The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens). 
# 1) bids, 2) total JA eps, 3) # tokens 4) TTR 
# Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs. control) and age in months as fixed effects and participant and specific video as random effects. 
# DV ~ age * condition + (1 | participant) + (1 | video)
# Lab standard operating procedures will be used for random effects pruning in case of non-convergence.
# We will interpret condition main effects as well as age * condition interactions (positive or negative) as evidence for behavior changes caused by video scaffolding. 
# Because of the larger number of coefficients of interest (4 models x 2 coefficients), we will adopt an alpha level of .005 for statistical significance and will report alpha between .05 and .005 as suggestive.
# “secondary analyses"
# We will analyze the proportion of coordinated vs. passive joint attention separately using the same model specification.

@@

We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
There was suggestively lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]). 
There was no significant effect of age, nor a significant interaction.
The preregistered regression predicting the number of tokens used by parents revealed no significant effects. 
An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

@@

As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% confidence intervals: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other significant effects on parental bids for JA.

@@

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that are strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "yellow", "take", and "put", while words that are most characteristic of the Science Video condition include "beep", "like", "say", "does", "uhoh", "for", and "neigh".

```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "The number of episodes of coordinated JA by condition and age in Experiment 2."}
# Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition. (no interpretation in PsychSci captions)

@@

This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from a commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), and then played with their child for three minutes using the same sets of toys given to those in the experimental conditions.
The quality of parents' interactions with their children were measured by the lexical diversity of their child-directed speech, and through behavioral coding of bids for and episodes of joint attention (JA).
